### 2019-06-13 NFES_Review/Chapters/_tbl_Collection.tex
NFES review progress

@@

%\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
%\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
%\cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
%\cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
%\cite{Duan2017}    \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.
%\cite{Gupta2007}   \\ %Novel Electrohydrodynamic Printing of Nanocomposite Biopolymer Scaffolds
%\cite{Huang2015}   \\ %Versatile, kinetically controlled, high precision electrohydrodynamic writing of micro/nanofibers
%\cite{Jiang2018}   \\ %Electrohydrodynamic Direct-Writing Micropatterns with Assisted Airflow
%\cite{Kim2018}     \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
\cite{Lee2012}     \\ %Fabrication of Patterned Nanofibrous Mats Using Direct-Write Electrospinning
\cite{Liu2014}     \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
\cite{Min2013}     \\ %Large-scale organic nanowire lithography and electronics
\cite{Pan2014}     \\ %Poly($\gamma$-benzyl $\alpha$, l-glutamate) in Cylindrical Near-Field Electrospinning Fabrication and Analysis of Piezoelectric Fibers
\cite{Pan2015}     \\ %Near-field electrospinning enhances the energy harvesting of hollow PVDF piezoelectric fibers
\cite{Song2015}    \\ %Patterned polydiacetylene-embedded polystyrene nanofibers based on electrohydrodynamic jet printing
\cite{Sun2006}     \\ %Near-Field Electrospinning
\cite{Wang2015}    \\ %Research on Multinozzle Near-Field Electrospinning Patterned Deposition
\cite{Wang2017}    \\ %Controllable deposition distance of aligned pattern via dual-nozzle near-field electrospinning
\cite{Wang2018}    \\ %Fabrication and evaluation of controllable deposition distance for aligned pattern by multi-nozzle near-field electrospinning
\cite{Xu2014}      \\ %Accuracy Improvement of Nano-fiber Deposition by Near-Field Electrospinning
\cite{Xue2014}     \\ %Rapid Patterning of 1-D Collagenous Topography as an ECM Protein Fibril Platform for Image Cytometry
\cite{Zheng2010}   \\ %Precision deposition of a nanofibre by near-field electrospinning
\cite{Zheng2014}   \\ %Electrohydrodynamic Direct-Write Orderly Micro/Nanofibrous Structure on Flexible Insulating Substrate
\cite{Zheng2012}   \\ %Polymer nanofibers prepared by low-voltage

>>>>

\hline
Fiber Characterization: &
\begin{itemize}[leftmargin=*]
\item A stack of fibers was produced, but fiber diameter is not reported.
\end{itemize} \\

\hline
Polymer(s): &
Polycaprolactone \\

\arrayrulecolor{lightgray}\hline
Solvent(s): &
Chloroform \\

\hline
NFES Variant: &
Direct-Write Electrospinning \\

\hline
Polymer Solution and Process Properties: &
\begin{itemize}[leftmargin=*]
\item Needle inner diameter: 200 $\mu m$
\item Ground electrode to collector plate distance: 50 $\mu m$
\item Solution concentration: 8.8 $w t \%$ Polycaprolactone
\item Solution stirred for 120 $min$
\item Applied voltage: 25 $k V$
\item Needle-to-collector distance: 70 $m m$
\item Solution flow rate: 0.1 $m L / h$
\item Electrospun at 23 $^\circ C$ and relative humidity between 54 and 57 \%
\item x-y stage velocity: 2-200 $m m / s$
\end{itemize} \\

\hline
Fiber Characterization: &
\begin{itemize}[leftmargin=*]
\item Fiber diameter: 400 $n m$ to 950 $\mu m$
\end{itemize} \\

\hline
Ref: & \cite{Lee2012} \\ %Fabrication of Patterned Nanofibrous Mats Using Direct-Write Electrospinning
\arrayrulecolor{black}\hline
\label{tbl:FloresCompare}
\end{tabular}
\end{center}
\end{table}
%----------------------------------------------------------------------%

\arrayrulecolor{lightgray}\hline
Solvent(s): &
Dimethyl Sulfoxide (DMSO)
    \begin{itemize}[leftmargin=*]
    \item Acetone and surfactant (ZONYL UR) were applied to improve the evaporation rate and to reduce the surface tension.
    \end{itemize} \\

\hline
NFES Variant: &
Hollow Cylindrical Near-Field Electrospinning (HCNFES) \\

\hline
Polymer Solution and Process Properties: &
\begin{itemize}[leftmargin=*]
\item Solution concentration: 16, 18, and 20 $w t \%$ PVDF
    \begin{itemize}[leftmargin=*]
    \item DMSO:acetone concentration is 1:1
    \item Surfactant amount: 0.2 $g$
    \end{itemize}
\item Solution preparation:
    \begin{itemize}[leftmargin=*]
    \item PVDF-acetone stirred for 30 $min$
    \item sufractant-DMSO stirred for 30 $min$
    \item Both solutions stirred for 60 $min$
    \end{itemize}
\item Needle-to-collector distance: 0.5 $m m$
\item Applied voltage: 10-16 $k V$
\item Tube collector rotational velocity: 900-1900 $rpm$
    \begin{itemize}[leftmargin=*]
    \item Tangential speed: 942.3-1989.3 $m m / s$
    \end{itemize}
\item Collector substrate: Poly(ethylene terephthalate) (PET)
\end{itemize} \\

@@

\hline
Ref: & \cite{Liu2014} \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
\arrayrulecolor{black}\hline
\label{tbl:FloresCompare}
\end{tabular}
\end{center}
\end{table}
%----------------------------------------------------------------------%

%\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
%\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
%\cite{Chang2008}   \\ %Continuous near-field electrospinning for large area deposition of orderly nanofiber patterns
%\cite{Dalton2015}  \\ % Additive manufacturing of scaffolds with sub-micron filaments via melt electrospinning writing Related content Patterned melt electrospun substrates for tissue engineering
%\cite{Duan2017}    \\ %Helix Electrohydrodynamic Printing of Highly Aligned Serpentine Micro/Nanofibers.
%\cite{Gupta2007}   \\ %Novel Electrohydrodynamic Printing of Nanocomposite Biopolymer Scaffolds
%\cite{Huang2015}   \\ %Versatile, kinetically controlled, high precision electrohydrodynamic writing of micro/nanofibers
%\cite{Jiang2018}   \\ %Electrohydrodynamic Direct-Writing Micropatterns with Assisted Airflow
%\cite{Kim2018}     \\ %Characterization of 3D electrospinning on inkjet printed conductive pattern on paper
%\cite{Lee2012}     \\ %Fabrication of Patterned Nanofibrous Mats Using Direct-Write Electrospinning
%\cite{Liu2014}     \\ %Direct-write PVDF nonwoven fiber fabric energy harvesters via the hollow cylindrical near-field electrospinning process
\cite{Min2013}     \\ %Large-scale organic nanowire lithography and electronics
\cite{Pan2014}     \\ %Poly($\gamma$-benzyl $\alpha$, l-glutamate) in Cylindrical Near-Field Electrospinning Fabrication and Analysis of Piezoelectric Fibers
\cite{Pan2015}     \\ %Near-field electrospinning enhances the energy harvesting of hollow PVDF piezoelectric fibers
\cite{Song2015}    \\ %Patterned polydiacetylene-embedded polystyrene nanofibers based on electrohydrodynamic jet printing
\cite{Sun2006}     \\ %Near-Field Electrospinning
\cite{Wang2015}    \\ %Research on Multinozzle Near-Field Electrospinning Patterned Deposition
\cite{Wang2017}    \\ %Controllable deposition distance of aligned pattern via dual-nozzle near-field electrospinning
\cite{Wang2018}    \\ %Fabrication and evaluation of controllable deposition distance for aligned pattern by multi-nozzle near-field electrospinning
\cite{Xu2014}      \\ %Accuracy Improvement of Nano-fiber Deposition by Near-Field Electrospinning
\cite{Xue2014}     \\ %Rapid Patterning of 1-D Collagenous Topography as an ECM Protein Fibril Platform for Image Cytometry
\cite{Zheng2010}   \\ %Precision deposition of a nanofibre by near-field electrospinning
\cite{Zheng2014}   \\ %Electrohydrodynamic Direct-Write Orderly Micro/Nanofibrous Structure on Flexible Insulating Substrate
\cite{Zheng2012}   \\ %Polymer nanofibers prepared by low-voltage
